---
title: "Group U_Final project"
author: "shiyun li, xia shan, junjie ma, peiyuan huo"
date: "4/25/2022"
output: html_document
---

#data preparing, choose a random sample of 2000 crimes happened during 2000-2022.
```{r}
library(readr)
library(DT)
library(dplyr)
crime=read.csv("/Users/apple/Desktop/dv/final/Crime_Data_from_2020_to_Present (1).csv")
```

#clean version of the total dataset
```{r}
col=c("DR_NO","Date.Rptd","Date.occ","TIME.OCC","AREA","AREA.NAME","Rpt.Dist.No","Crm.Cd.Desc","Mocodes",
      "Vict.Age","Vict.Sex","Vict.Descent","Premis.Desc","Weapon.Desc","Status.Desc","LOCATION","LAT","LON")
clean_total=crime[,colnames(crime) %in% col]

clean_total$TIME.OCC <- as.character(clean_total$TIME.OCC) 
proper_case <- function(x) {
  return (gsub("\\b([A-Z])([A-Z]+)", "\\U\\1\\L\\2" , x, perl=TRUE))
}
clean_total <- clean_total %>% mutate(Crm.Cd.Desc = proper_case(Crm.Cd.Desc),
                    AREA=proper_case(AREA),
                    AREA.NAME=proper_case(AREA.NAME),
                    LOCATION=proper_case(LOCATION),
                    Weapon.Desc = proper_case(Weapon.Desc),
                    Premis.Desc=proper_case(Premis.Desc),
                    Status.Desc=proper_case(Status.Desc))
```

#delete the cases that are still under investigation
```{r}
sum_ctg=clean_total %>% 
  group_by(Status.Desc)%>%
  summarise(length(Status.Desc))

total1=subset(clean_total,Status.Desc=="Adult Arrest"|Status.Desc=="Adult Other" |Status.Desc=="Juv Arrest"|Status.Desc=="Juv Other")
```

#integragate crime category
```{r}
sum_crime=total1 %>% 
  group_by(Crm.Cd.Desc)%>%
  summarise(length(Crm.Cd.Desc))
#select the cirmes that happen more than 500 times 
clean_total=subset(total1,Crm.Cd.Desc=="Intimate Partner - Simple Assault"|Crm.Cd.Desc=="Battery - Simple Assault"|Crm.Cd.Desc=="Assault With Deadly Weapon, Aggravated Assault
"|Crm.Cd.Desc=="	Vandalism - Felony ($400 & Over, All Church Vandalisms) "|Crm.Cd.Desc=="Intimate Partner - Aggravated Assault"|Crm.Cd.Desc=="Criminal Threats - No Weapon Displayed"|Crm.Cd.Desc=="Robbery"|Crm.Cd.Desc=="Vehicle-Stolen"|Crm.Cd.Desc=="Burglary"|Crm.Cd.Desc=="Violation Of Restraining Order "|Crm.Cd.Desc=="Brandish Weapon "|Crm.Cd.Desc==" Vandalism - Misdeameanor ($399 Or Under)"|Crm.Cd.Desc=="Violation Of Court Order "|Crm.Cd.Desc==" Theft Plain - Petty ($950 & Under)"|Crm.Cd.Desc==" Letters, Lewd  -  Telephone Calls, Lewd"|Crm.Cd.Desc=="Child Abuse (Physical) - Simple Assault "|Crm.Cd.Desc=="Theft-Grand ($950.01 & Over)Excpt,Guns,Fowl,Livestk,Prod "|Crm.Cd.Desc==" Trespassing"|Crm.Cd.Desc=="Other Miscellaneous Crime "|Crm.Cd.Desc=="Contempt Of Court "|Crm.Cd.Desc==" Shoplifting - Petty Theft ($950 & Under)"|Crm.Cd.Desc==" Attempted Robbery"|Crm.Cd.Desc==" Battery Police (Simple)
"|Crm.Cd.Desc=="Battery With Sexual Contact "|Crm.Cd.Desc=="Rape, Forcible "|Crm.Cd.Desc=="	
Other Assault "|Crm.Cd.Desc==" 	Burglary From Vehicle"|Crm.Cd.Desc=="Embezzlement, Grand Theft ($950.01 & Over) "|Crm.Cd.Desc==" 	Theft Of Identity")
```

#use datatable to show the first 100 cases
```{r}
sample=clean_total[1:100, ]
datatable(sample, options = list(pageLength = 5,scrollX='400px'))
```

#visualize the crime
# Preprocessing
```{r}
library(tidyverse)
library("lubridate")

clean_total <- clean_total %>%
  mutate(Date = as.Date(Date.Rptd, "%m/%d/%Y %H:%M:%S")) %>%
  mutate(Location = str_squish(LOCATION))

names(clean_total)[names(clean_total) == 'Crm.Cd.Desc'] <- "Category"
clean_total$Year <- format(clean_total$Date, format="%Y")
```

# Map
```{r}
library(leaflet)

clean_total <- clean_total[clean_total$LON != 0, ] # display the first 10,000 rows
clean_total$popup <- paste("<br>", "<b>Category: </b>", clean_total$Category,
                    "<br>", "<b>Date: </b>", clean_total$Date,
                    "<br>", "<b>Address: </b>", clean_total$Location,
                    "<br>", "<b>Vict Age: </b>", clean_total$Vict.Age,
                    "<br>", "<b>Vict Sex: </b>", clean_total$Vict.Sex,
                    "<br>", "<b>Longitude: </b>", clean_total$LON,
                    "<br>", "<b>Latitude: </b>", clean_total$LAT)

leaflet(clean_total, width = "100%") %>% addTiles() %>%
  addTiles(group = "OSM (default)") %>%
  addProviderTiles(provider = "Esri.WorldStreetMap",group = "World StreetMap") %>%
  addProviderTiles(provider = "Esri.WorldImagery",group = "World Imagery") %>%
  # addProviderTiles(provider = "NASAGIBS.ViirsEarthAtNight2012",group = "Nighttime Imagery") %>%
  addMarkers(lng = ~LON, lat = ~LAT, popup = clean_total$popup, clusterOptions = markerClusterOptions()) %>%
  addLayersControl(
    baseGroups = c("OSM (default)","World StreetMap", "World Imagery"),
    options = layersControlOptions(collapsed = FALSE)
  )

```

# aggregte data

```{r}
df=read.csv("/Users/apple/Desktop/dv/final/clean_total.csv")
```

Summarize the data by crime category.
```{r}
library(DT)
library(stringr)
Sys.setlocale("LC_TIME", "C")
df_category <- sort(table(df$Crm.Cd.Desc),decreasing = TRUE)
df_category <- data.frame(df_category)
colnames(df_category) <- c("Category", "Frequency")
df_category$Percentage <- df_category$Frequency / sum(df_category$Frequency)
datatable(df_category, options = list(scrollX='400px'))
```

Create a bar plot based on the crime category.
```{r}
library(ggplot2)
library(ggrepel)
bp <- ggplot(df_category, aes(x=Category, y=Frequency, fill=Category)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x=element_blank()) + 
  geom_text_repel(data=df_category, aes(label=Category), size=2)
bp
```

Create a pie chart based on the crime category.
```{r}
bp <- ggplot(df_category, aes(x="", y=Percentage, fill=Category)) +
  geom_bar(stat="identity") + 
  coord_polar("y") 
bp
```

## Temporal Trends
### Robbery Over Time
Create a chart of crimes (Robbery) over time.
```{r}
df_robbery <- df[df$Crm.Cd.Desc == "Robbery",]

df_robbery_daily <- df_robbery %>%
  mutate(Date = as.Date(Date.Rptd, "%m/%d/%Y %H:%M:%S")) %>%
  group_by(Date) %>%
  summarize(count = n()) %>%
  arrange(Date)

library(ggplot2)
library(scales)

plot <- ggplot(df_robbery_daily, aes(x = Date, y = count)) +
  geom_line(color = "#F2CA27", size = 0.1) +
  geom_smooth(color = "#1A1A1A") +
  # fte_theme() +
  scale_x_date(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  labs(x = "Date of Robbery", y = "Number of Robberys", title = "Daily Robberys From 2020 to 2022")
plot
```

### Robbery Time Heatmap
```{r}
library(lubridate)

get_hour <- function(x) {
  return (as.numeric((str_split(str_split(x, " ", simplify = T)[,2], ":", simplify = T)[,1])))
}

get_weekdays <- function(x){
  return (weekdays(as.Date(x, format = "%m/%d/%Y %H:%M:%S")))
}

df_robbery_time <- df_robbery %>%
  mutate(Hour = sapply(Date.Rptd, get_hour)) %>%
  mutate(DayOfWeek = sapply(Date.Rptd, get_weekdays)) %>%
  group_by(DayOfWeek, Hour) %>%
  summarize(count = n())
# df_theft_time %>% head(10)
datatable(df_robbery_time, options = list(scrollX='400px'))
```

```{r}
plot <- ggplot(df_robbery_time, aes(x = Hour, y = DayOfWeek, fill = count)) +
  geom_tile() +
  # fte_theme() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6), legend.title = element_blank(), legend.position="top", legend.direction="horizontal", legend.key.width=unit(2, "cm"), legend.key.height=unit(0.25, "cm"), legend.margin=unit(-0.5,"cm"), panel.margin=element_blank()) +
  labs(x = "Hour of Roberry (Local Time)", y = "Day of Week of Roberry", title = "Number of Roberry from 2020 to 2022, by Time of Roberry") +
  scale_fill_gradient(low = "white", high = "#27AE60", labels = comma)
plot
```

### Robbery Over Time
Create a chart of crimes (Burglary) over time.
```{r}
df_burglary <- df[df$Crm.Cd.Desc == "Burglary",]

df_burglary_daily <- df_burglary %>%
  mutate(Date = as.Date(Date.Rptd, "%m/%d/%Y %H:%M:%S")) %>%
  group_by(Date) %>%
  summarize(count = n()) %>%
  arrange(Date)

library(ggplot2)
library(scales)

plot <- ggplot(df_burglary_daily, aes(x = Date, y = count)) +
  geom_line(color = "#F2CA27", size = 0.1) +
  geom_smooth(color = "#1A1A1A") +
  # fte_theme() +
  scale_x_date(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  labs(x = "Date of Burglary", y = "Number of Burglarys", title = "Daily Burglarys From 2020 to 2022")
plot
```

```{r}
df_burglary_time <- df_burglary %>%
  mutate(Hour = sapply(Date.Rptd, get_hour)) %>%
  mutate(DayOfWeek = sapply(Date.Rptd, get_weekdays)) %>%
  group_by(DayOfWeek, Hour) %>%
  summarize(count = n())

plot <- ggplot(df_burglary_time, aes(x = Hour, y = DayOfWeek, fill = count)) +
  geom_tile() +
  # fte_theme() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6), legend.title = element_blank(), legend.position="top", legend.direction="horizontal", legend.key.width=unit(2, "cm"), legend.key.height=unit(0.25, "cm"), legend.margin=unit(-0.5,"cm"), panel.margin=element_blank()) +
  labs(x = "Hour of Burglary (Local Time)", y = "Day of Week of Burglary", title = "Number of Burglary from 2020 to 2022, by Time of Burglary") +
  scale_fill_gradient(low = "white", high = "#27AE60", labels = comma)
plot
```

#correlation analysis

```{r}
library(magrittr)
library(dplyr)
library(DT)
library(ggplot2)
library(gridExtra)
library(grid)
```

```{r}
df=read.csv("/Users/apple/Desktop/dv/final/clean_total.csv")
# Convert date formate
df$date <- substr(df$Date.Rptd,1,10)
betterDates <- as.Date(df$date, "%m/%d/%y")

df$DayOfWeek <- weekdays(betterDates)

```

## Crime By Category
```{r}
df_arrest <- df %>% filter(grepl("Arrest", Status.Desc))
df_top_crimes <- df_arrest %>%
  group_by(Crm.Cd.Desc) %>% 
  summarize(count = n()) %>%
  arrange(desc(count))

datatable(df_top_crimes, options = list(pageLength = 10,scrollX='400px'))
```

```{r}
# Define a function that will conver Time.Occ to two-digit time indicator
# For instance, 1245 will return 12, 25 will return 0, and 345 will return 3
ToTime <- function(x){
  if ((floor(log10(x)) + 1)<=2){
    result <- "0"
  } else if (floor(log10(x)) + 1==3){
    result <- substr(x, 1, 1)
  } else {
    result <- substr(x, 1, 2)
  }
  return (result)
}

```


## By Category
```{r}
df_arrest_time_crime <- df_arrest %>%
  filter(Crm.Cd.Desc %in% df_top_crimes$Crm.Cd.Desc[2:19]) %>%
  mutate(Hour = sapply(TIME.OCC, ToTime)) %>%
  group_by(Crm.Cd.Desc, DayOfWeek, Hour) %>% 
  summarize(count = n())

dow_format <- c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
hour_format <- c(paste(c(12,1:11),"AM"), paste(c(12,1:11),"PM"))

df_arrest_time_crime$DayOfWeek <- factor(df_arrest_time_crime$DayOfWeek, level = rev(dow_format))
df_arrest_time_crime$Hour <- factor(df_arrest_time_crime$Hour, level = 0:23, label = hour_format)

datatable(df_arrest_time_crime, options = list(pageLength = 10, scrollX='400px'))
```



```{r}

plot <- ggplot(df_arrest_time_crime, aes(x = Hour, y = DayOfWeek, fill = count)) +
  geom_tile() +
  # fte_theme() +
  theme(axis.text=element_text(size=8), axis.text.x = element_text(angle = 90, vjust = 0.6, size = 8)) +
  labs(x = "Hour of Arrest (Local Time)", y = "Day of Week of Arrest", title = "Number of Police Arrests in Los Angeles from 2020 – Present, by Category and Time of Arrest") +
  scale_fill_gradient(low = "white", high = "#2980B9") +
  facet_wrap(~ Crm.Cd.Desc, nrow = 3)
plot

```
## By Category (Normalized)
```{r}
df_arrest_time_crime <- df_arrest_time_crime %>%
  group_by(Crm.Cd.Desc) %>%
  mutate(norm = count/sum(count))

datatable(df_arrest_time_crime, options = list(pageLength = 10,scrollX='400px'))

plot <- ggplot(df_arrest_time_crime, aes(x = Hour, y = DayOfWeek, fill = norm)) +
  geom_tile() +
  # fte_theme() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, size = 8)) +
  labs(x = "Hour of Arrest (Local Time)", y = "Day of Week of Arrest", title = "Police Arrests in Los Angeles from 2020 by Time of Arrest, Normalized by Type of Crime") +
  scale_fill_gradient(low = "white", high = "#2980B9") +
  facet_wrap(~ Crm.Cd.Desc, nrow = 3)
plot


```
## By Police District
```{r}
df_arrest_time_district <- df_arrest %>%
  mutate(Hour = sapply(TIME.OCC, ToTime)) %>%
  group_by(AREA.NAME, DayOfWeek, Hour) %>% 
  summarize(count = n()) %>%
  group_by(AREA.NAME) %>%
  mutate(norm = count/sum(count))

df_arrest_time_district$DayOfWeek <- factor(df_arrest_time_district$DayOfWeek, level = rev(dow_format))
df_arrest_time_district$Hour <- factor(df_arrest_time_district$Hour, level = 0:23, label = hour_format)

datatable(df_arrest_time_district, options = list(pageLength = 10,scrollX='400px'))
```
```{r}
plot <- ggplot(df_arrest_time_district, aes(x = Hour, y = DayOfWeek, fill = norm)) +
  geom_tile() +
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.6, size =4)) +
  labs(x = "Hour of Arrest (Local Time)", y = "Day of Week of Arrest", title = "Police Arrests in Los Angeles from 2020 by Time of Arrest, Normalized by Station") +
  scale_fill_gradient(low = "white", high = "#8E44AD") +
  facet_wrap(~ AREA.NAME, nrow=5,shrink=FALSE) 
plot



```

## By Month
```{r}
df_arrest_time_month <- df_arrest %>%
  mutate(Month = format(as.Date(date, "%m/%d/%Y"), "%B"), Hour = sapply(TIME.OCC, ToTime)) %>%
  group_by(Month, DayOfWeek, Hour) %>% 
  summarize(count = n()) %>%
  group_by(Month) %>%
  mutate(norm = count/sum(count))

df_arrest_time_month$DayOfWeek <- factor(df_arrest_time_month$DayOfWeek, level = rev(dow_format))
df_arrest_time_month$Hour <- factor(df_arrest_time_month$Hour, level = 0:23, label = hour_format)

# Set order of month facets by chronological order instead of alphabetical
df_arrest_time_month$Month <- factor(df_arrest_time_month$Month,
                                     level = c("January","February","March","April","May","June","July","August","September","October","November","December"))

plot <- ggplot(df_arrest_time_month, aes(x = Hour, y = DayOfWeek, fill = norm)) +
  geom_tile() +
  # fte_theme() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, size = 4)) +
  labs(x = "Hour of Arrest (Local Time)", y = "Day of Week of Arrest", title = "Police Arrests in Los Angeles from 2020 by Time of Arrest, Normalized by Month") +
  scale_fill_gradient(low = "white", high = "#E74C3C") +
  facet_wrap(~ Month, nrow = 4)
plot
```

## By Year
```{r}
df_arrest_time_year <- df_arrest %>%
  mutate(Year = format(as.Date(date(), "%m/%d/%Y"), "%Y"), Hour = sapply(TIME.OCC, ToTime)) %>%
  group_by(Year, DayOfWeek, Hour) %>% 
  summarize(count = n()) %>%
  group_by(Year) %>%
  mutate(norm = count/sum(count))

df_arrest_time_year$DayOfWeek <- factor(df_arrest_time_year$DayOfWeek, level = rev(dow_format))
df_arrest_time_year$Hour <- factor(df_arrest_time_year$Hour, level = 0:23, label = hour_format)

plot <- ggplot(df_arrest_time_year, aes(x = Hour, y = DayOfWeek, fill = norm)) +
  geom_tile() +
  # fte_theme() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, size = 4)) +
  labs(x = "Hour of Arrest (Local Time)", y = "Day of Week of Arrest", title = "Police Arrests Los Angeles from 2020 by Time of Arrest, Normalized by Year") +
  scale_fill_gradient(low = "white", high = "#E67E22") +
  facet_wrap(~ Year, nrow = 6)
plot
```


